### 2015-08-14 writing/SNLI paper/entailment_eval.tex
New learning curve.

\Fig{learning_curves_bow.pdf}{0.45}{bowlearncurve}{
A learning curve for the lexicalized and unlexicalized baseline classifiers and the LSTM,
plotted on a log scale. The y-axis starts at a random-chance accuracy of 33\%. The minibatch size of 64 that we used to tune the LSTM sets a lower bound on data for that model.}

>>>>

\Fig{new_lcc.pdf}{0.83}{bowlearncurve}{
A learning curve showing how the baseline classifiers and the LSTM perform when trained to convergence on varied amounts of training data. The y-axis starts near a random-chance accuracy of 33\%. The minibatch size of 64 that we used to tune the LSTM sets a lower bound on data for that model.}
